Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2015-02-15 doc/GMP2015/original_submission/appendix_b.tex
Made dir for original submission. Made dir for revision one and got it to compile with the new class file.

\subsection{Furture Work}
\label{sec:futurework}
A few natural  open questions are the following.
The first 2 are from Section \ref{sec:recomb}.

\begin{openproblem}
    Combinatorial rigidity for
    periodic structures is an active area of research. This paper motivates
    a study of the rigidity of self-similar structures,
    with self-similar groups replacing periodic groups.
\end{openproblem}

\begin{openproblem}
What is the complexity of the restricted OMD (optimal modification for
decomposition) problem?
This has the potential to be difficult. For example, when the
isostatic completion is required to be a 2-tree the restricted OMD
problem is reducible to the maximum spanning series-parallel subgraph
problem shown by \cite{cai1993spanning} to be NP-complete even if the input
graph is planar of maximum degree at most 6. However, since the OMD
problem has other input restrictions such as not having any proper
isostatic subgraphs, it is not clear if the reverse reduction exists
and hence it is unclear whether the OMD problem is NP-complete.

The next is the reverse direction of Observation \ref{obs:OC_to_OMD} in Section \ref{sec:table}.

\begin{openproblem}
    Is the OMD (optimal modification for decomposition) problem
    reducible to the OC (Optimal completion) problem?
\end{openproblem}

The last problem is from
Section \ref{sec:bodypin}.

\begin{openproblem}
    What is the complexity of the optimal completion problem when the given
    graph has more than 2-dofs?
    Our proof for the 1 and 2-dof cases relied heavily on the matroidal
    properties of their corresponding $(k,l)$-tightness.
    For higher number of dofs, the $(k,l)$ characterization is
    no longer matroidal \cite{Lee:2007:PGA}.
    As a result, the major obstacle is that
    there is no easy way of obtaining an optimal or canonical
    $k$-dof DR-plan in general.
    Even assuming such  a DR-plan is available,
    if higher dofs had the same characteristics,
    Observation \ref{obs:algebraic_completion}
    raises questions about the correct measure of DR-plan size that
    captures algebraic complexity for recombining graphs with many dofs
    (this is not an issue in the isostatic case). Unless some restrictions
    can be found and taken advantage of, the $k$-dof optimal
    completion problem would  have complexity exponential in $k$.
\end{openproblem}

\subsection{Open Problems}

\todo{added these in newest conclusion}

@@

The next is the reverse direction of Observation \ref{obs:OC_to_OMD} in
Section \ref{sec:table}.

\begin{openproblem}
    Is the OMD (optimal modification for decomposition) problem
    reducible to the OC (Optimal completion) problem?
\end{openproblem}

@@

>>>>

\subsection{Open Problems}
\label{sec:futurework}

One open problem comes from Section \ref{sec:DRP}:
\begin{openproblem}
    Is there a lower complexity algorithm than \candrpcomplexityv to find the canonical DR-plan of isostatic 2D bar-joint graphs?
\end{openproblem}

@@

The next is the reverse direction of Observation \ref{obs:OC_to_OMD} in Section \ref{sec:table}.
\begin{openproblem}
    Is the OMD (optimal modification for decomposition) problem reducible to the OC (Optimal completion) problem?
\end{openproblem}

@@

\begin{openproblem}
    Experimental validation (either computationally or physical experiments) of predications based on the material model and theory used in this paper. This can be done by modeling known materials and putting stresses on them, seeing if the prediction is observed in the real material. Or, our theory could be used to design new materials, which can be tested to see if they possess predicted properties.
\end{openproblem}

### 2015-02-15 doc/GMP2015/original_submission/s01_introduction.tex
Made dir for original submission. Made dir for revision one and got it to compile with the new class file.

Some properties of natural and engineered materials can be analyzed by
treating them as two dimensional (2D) layers. As illustrated by the
examples below, the structure within each layer is often self-
similar~\cite{2012arXiv1204.6389G} spanning multiple scales; generally
aperiodic and quasi-uniform within any one scale; and consists of a
few repeated motifs appearing in disordered arrangements. Each layer
is not necessarily planar, i.e., it consists of multiple, inter-
constraining planar (genus 0) monolayers. Furthermore, a layer is
often  either \vemph{isostatic or under-constrained, not self-
stressed} (See Section \ref{sec:prelim} for definitions). These
properties are consistent with a self-assembled 2D structure that
minimizes mass, optimally distributes external stresses and itself
participates in the assembly of diverse and multifunctional, larger 2D
structures.

@@

\medskip\noindent
\header{(v) Configuration Spaces of Under-constrained Systems.}
For under-constrained 2D bar-joint and body-hyperpin qusecs obtained
from various subclasses of tree-decomposable systems, algorithms have
been developed to complete them into isostatic systems
\cite{joan-arinyo2003transforming,sitharam2005combinatorial,gao2006ctree,sitharam2010convex} and to find paths within the connected components
\cite{sitharam2011cayleyI,hidalgo2011reachability} of standard Cartesian configuration spaces.
Most of the
algorithms with formal guarantees leverage Cayley configuration space
theory \cite{sitharam2010convex,sitharam2011cayleyI,sitharam2011cayleyII} to characterize subclasses of graphs and
additional constraints that control combinatorial explosion, and
provide faithful bijective representation of connected components and
paths. These algorithms have decreasing efficiency as the subclass of
systems gets bigger, with highest efficiency for underlying partial
2-tree graphs (alternately called, tree-width 2, series-parallel, $K_4$
minor avoiding), moderate efficiency for 1 degree- of-freedom (dof)
graphs with low Cayley complexity (which include common linkages such
as the Strandbeest, Limacon and Cardioid), and decreased efficiency
for general 1-dof tree-decomposable graphs. While software suites
exist  \cite{keycurriculum1995geometer,porta2014open,siemens1999d,todd2007geometry}, no such formal algorithms and guarantees are known
for non-tree-decomposable systems.
%
\subsection{Contributions and Organization}
\label{sec:cont}

The contributions of this paper are the following.
\begin{itemize}
  \item In Section \ref{sec:DRP}, we navigate the NP-hardness barrier mentioned in (2) above,
  for finding optimal DR-plans by defining a so-called \dfn{canonical}
  DR-plan and showing a strong Church-Rosser property: \vemph{all
  canonical DR-plans for isostatic or under-constrained 2D qusecs are
  optimal}.

@@

  \item In Section \ref{sec:recomb}, we give a method to deal with the
  algebraic complexity of recombining the realizations or solutions of
  child subsystems into a solution of the parent system
  \cite{sitharam2010optimized,sitharam2006well,sitharam2010reconciling}
  Specifically, we define the problem of minimally modifying the
  indecomposable recombination system so that it becomes decomposable
  via a small DR-plan and yet preserves the original solutions in an
  efficiently searchable manner. In Section \ref{sec:table}, we show formal connection to well
  known problems such as optimal completion of under-constrained
  systems
  \cite{joan-arinyo2003transforming,sitharam2005combinatorial,gao2006ctree}
  and to find paths within the connected components. When the
  modifications are bounded, we obtain new, efficient algorithms for
  realizing both isostatic and under-constrained qusecs by leveraging
  recent results about Cayley parameters in
  \cite{sitharam2010convex,sitharam2011cayleyI,sitharam2011cayleyII} (see Sections \ref{sec:2-tree-reduction} and \ref{sec:tdecomp}).

@@

\noindent
\note All proofs appear in Appendix A (\ref{sec:appendix:a}).

>>>>

Some properties of natural and engineered materials can be analyzed by
treating them as two dimensional (2D) layers. As illustrated by the
examples below, the structure within each layer is often self-
similar~\cite{2012arXiv1204.6389G} spanning multiple scales; generally
aperiodic and quasi-uniform within any one scale; and consists of a
few repeated motifs appearing in disordered arrangements. Each layer
is not necessarily planar, i.e., it consists of multiple, inter-
constraining planar (genus 0) monolayers. Furthermore, a layer is
often  either \vemph{isostatic or underconstrained, not self-
stressed} (See Section \ref{sec:prelim} for definitions). These
properties are consistent with a self-assembled 2D structure that
minimizes mass, optimally distributes external stresses and itself
participates in the assembly of diverse and multifunctional, larger 2D
structures.

@@

\medskip\noindent
\header{(v) Configuration Spaces of Underconstrained Systems.}
For underconstrained 2D bar-joint and body-hyperpin qusecs obtained
from various subclasses of tree-decomposable systems, algorithms have
been developed to complete them into isostatic systems
\cite{joan-arinyo2003transforming,sitharam2005combinatorial,gao2006ctree,sitharam2010convex} and to find paths within the connected components
\cite{sitharam2011cayleyI,hidalgo2011reachability} of standard Cartesian configuration spaces.
Most of the
algorithms with formal guarantees leverage Cayley configuration space
theory \cite{sitharam2010convex,sitharam2011cayleyI,sitharam2011cayleyII} to characterize subclasses of graphs and
additional constraints that control combinatorial explosion, and
provide faithful bijective representation of connected components and
paths. These algorithms have decreasing efficiency as the subclass of
systems gets bigger, with highest efficiency for underlying partial
2-tree graphs (alternately called, tree-width 2, series-parallel, $K_4$
minor avoiding), moderate efficiency for 1 degree- of-freedom (dof)
graphs with low Cayley complexity (which include common linkages such
as the Strandbeest, Limacon and Cardioid), and decreased efficiency
for general 1-dof tree-decomposable graphs. While software suites
exist  \cite{keycurriculum1995geometer,porta2014open,siemens1999d,todd2007geometry}, no such formal algorithms and guarantees are known
for non-tree-decomposable systems.
%
\subsection{Contributions and Organization}
\label{sec:cont}

The contributions of this paper are the following.
\begin{itemize}
  \item In Section \ref{sec:DRP}, we navigate the NP-hardness barrier mentioned in (2) above,
  for finding optimal DR-plans by defining a so-called \dfn{canonical}
  DR-plan and showing a strong Church-Rosser property: \vemph{all
  canonical DR-plans for isostatic or underconstrained 2D qusecs are
  optimal}.

@@

  \item In Section \ref{sec:recomb}, we give a method to deal with the
  algebraic complexity of recombining the realizations or solutions of
  child subsystems into a solution of the parent system
  \cite{sitharam2010optimized,sitharam2006well,sitharam2010reconciling}
  Specifically, we define the problem of minimally modifying the
  indecomposable recombination system so that it becomes decomposable
  via a small DR-plan and yet preserves the original solutions in an
  efficiently searchable manner. In Section \ref{sec:table}, we show formal connection to well
  known problems such as optimal completion of underconstrained
  systems
  \cite{joan-arinyo2003transforming,sitharam2005combinatorial,gao2006ctree}
  and to find paths within the connected components. When the
  modifications are bounded, we obtain new, efficient algorithms for
  realizing both isostatic and underconstrained qusecs by leveraging
  recent results about Cayley parameters in
  \cite{sitharam2010convex,sitharam2011cayleyI,sitharam2011cayleyII} (see Sections \ref{sec:2-tree-reduction} and \ref{sec:tdecomp}).

@@

\noindent
\note All proofs appear in the Appendix (submitted an a permitted attachment via EasyChair).

### 2015-02-15 doc/GMP2015/original_submission/s03_drp.tex
Made dir for original submission. Made dir for revision one and got it to compile with the new class file.

\section{The canonical DR-plan}
\label{sec:DRP}
% In the problem of the optimal DR-Plan there is generally not a unique plan.
% % Indeed, we will prove a union of $N$ well-constrained subgraphs will result in $N$ unique plans, but that at the $N^{\text{th}}$ level of the tree it will always be the same. Therefore, all choices of decomposition are in some sense equivalent. The theorem we seek to prove is thus:
% However, we will show that regardless of which children are chosen for the plan, so long as they satisfy the definition of an optimal DR-plan, the recombination will require solving of the same systems. Being the smallest such structure that offers this, the definition of an optimal DR-plan could be considered the canonical DR-plan.
% % To assist in showing this, we prove this core theorem throughout this section:

% In this section, we discuss 2D bar-joint graphs. All vertex weights are $2$, all edge weights are $1$, and constant $k= -{{3}\choose{2}}=-3$. Trivial graphs are a single vertex and empty set. Furthermore, 2D well-constrained graphs must be connected.
% % The greatest density of a 2D well-constrained graph is $-2$ (the vertex). The other disconnected part of the graph would need to have a density of $-1$, which is over-constrained and not possible in a well-constrained graph (because there is no trivial graph with that density).

@@

\begin{definition}
    The \dfn{canonical DR-plan} is a DR-plan that satisfies the following two properties:
    (1) children are isostatic vertex-maximal subgraphs of the parent; and
    (2) all of the isostatic vertex-maximal subgraphs are children if any two of them intersect trivially, otherwise exactly two are children.
\end{definition}

@@

%\begin{theorem}\label{theorem:main}
%Given an isostatic 2D bar-joint graph $G$ and ComDRP$(G)$, for all nodes $C$
%with children $C_1,\ldots,C_N$ preserve children according to the following rules.
%\begin{enumerate}
%    \item If $C_i \cap C_j$ is trivial then keep all $C_1,\ldots,C_N$ as children.
%    \item If $C_i \cap C_j$ is isostatic then select any two out of $C_1,\ldots,C_N$ as children.
%\end{enumerate}
%The resulting canonical DR-plan is an optimal DR-plan.
%\end{theorem}

@@

\begin{observation}\label{lemma:union_intersection}
If $F_i$ and $F_j$ are isostatic subgraphs of the same
isostatic graph $F$, \
then the following hold:
(1) $F_i\cup F_j$ is not trivial;
(2) $F_i\cup F_j$ is under-constrained if and only if $F_i\cap F_j$ is trivial;
(3) $F_i\cup F_j$ is well-constrained if and only if $F_i\cap F_j$ is well-constrained; and
(4) $F_i\cap F_j$ is not under-constrained.
\end{observation}

@@

\myexample
\textsl{[DR-Plan for self-similar structure]}
This section details the decomposition of the graph in Figure \ref{fig:c2c3ofk33s}. The graph $G$ has only two isostatic vertex-maximal subgraphs, $G$ without the outermost triangle composed of $K_{3,3}$ graphs (triangle $1$) and $G$ without the inner triangle $N$. These intersect on $G$ without triangle $1$ and $N$ which is clearly well-constrained. As explained in the proof of Theorem \ref{theorem:main} since there are only 2 possible children, their intersection must be a node 2 levels below the parent. Just as expected, it is on the third level, as it is a child of both of $G$'s children. Furthermore, it intersects trivially with the edges that connect triangle $1$ and $N$ to $2$ and $N-1$, respectively; these necessarily intersect with triangle $1$ and $N$ themselves trivially (by Theorem \ref{theorem:main}, part 1) making all of these children. The triangles then decompose into their constituent $K_{3,3}$ graphs, which then decompose into 9 edges.

>>>>

\section{The canonical DR-plan}
\label{sec:DRP}
% In the problem of the optimal DR-Plan there is generally not a unique plan.
% % Indeed, we will prove a union of $N$ isostatic subgraphs will result in $N$ unique plans, but that at the $N^{\text{th}}$ level of the tree it will always be the same. Therefore, all choices of decomposition are in some sense equivalent. The theorem we seek to prove is thus:
% However, we will show that regardless of which children are chosen for the plan, so long as they satisfy the definition of an optimal DR-plan, the recombination will require solving of the same systems. Being the smallest such structure that offers this, the definition of an optimal DR-plan could be considered the canonical DR-plan.
% % To assist in showing this, we prove this core theorem throughout this section:

% In this section, we discuss 2D bar-joint graphs. All vertex weights are $2$, all edge weights are $1$, and constant $k= -{{3}\choose{2}}=-3$. Trivial graphs are a single vertex and empty set. Furthermore, 2D isostatic graphs must be connected.
% % The greatest density of a 2D isostatic graph is $-2$ (the vertex). The other disconnected part of the graph would need to have a density of $-1$, which is overconstrained and not possible in a isostatic graph (because there is no trivial graph with that density).

@@

\begin{definition}\label{def:canonical_drplan}
    The \dfn{canonical DR-plan} satisfies the following three properties:
    (1) it is a DR-plan;
    (2) children are rigid vertex-maximal proper subgraphs of the parent; and
    (3) if all pairs of rigid vertex-maximal proper subgraphs intersect trivially then all of them are children, otherwise take as children exactly two that intersect non-trivially.
\end{definition}

@@

%\begin{theorem}\label{theorem:main}
%Given an isostatic 2D bar-joint graph $G$ and ComDRP$(G)$, for all nodes $C$
%with children $C_1,\ldots,C_N$ preserve children according to the following rules.
%\begin{enumerate}
%    \item If $C_i \cap C_j$ is trivial then keep all $C_1,\ldots,C_N$ as children.
%    \item If $C_i \cap C_j$ is isostatic then select any two out of $C_1,\ldots,C_N$ as children.
%\end{enumerate}
%This is a canonical DR-plan.
%\end{theorem}

@@

\begin{observation}\label{lemma:union_intersection}
If $F_i$ and $F_j$ are isostatic subgraphs of the same
isostatic graph $F$, \
then the following hold:
(1) $F_i\cup F_j$ is not trivial;
(2) $F_i\cup F_j$ is underconstrained if and only if $F_i\cap F_j$ is trivial;
(3) $F_i\cup F_j$ is isostatic if and only if $F_i\cap F_j$ is isostatic; and
(4) $F_i\cap F_j$ is not underconstrained.
\end{observation}

@@

\myexample
\textsl{[DR-Plan for self-similar structure]}
This section details the decomposition of the graph in Figure \ref{fig:c2c3ofk33s}. The graph $G$ has only two isostatic vertex-maximal subgraphs, $G$ without the outermost triangle composed of $K_{3,3}$ graphs (triangle $1$) and $G$ without the inner triangle $N$. These intersect on $G$ without triangle $1$ and $N$ which is clearly isostatic. As explained in the proof of Theorem \ref{theorem:main} since there are only 2 possible children, their intersection must be a node 2 levels below the parent. Just as expected, it is on the third level, as it is a child of both of $G$'s children. Furthermore, it intersects trivially with the edges that connect triangle $1$ and $N$ to $2$ and $N-1$, respectively; these necessarily intersect with triangle $1$ and $N$ themselves trivially (by Theorem \ref{theorem:main}, part 1) making all of these children. The triangles then decompose into their constituent $K_{3,3}$ graphs, which then decompose into 9 edges.

### 2015-02-15 doc/GMP2015/original_submission/s05_problems.tex
Made dir for original submission. Made dir for revision one and got it to compile with the new class file.

%In the recombination setting, the corresponding \dfn{restricted
%OMD$_k$  problem} requires the reduced graph $G'$ and its isostatic
%completion $H$ to be 2-trees as in Section \ref{sec:2-tree-reduction}
%or to be a low Cayley complexity tree-decomposable graph as in Section
%\ref{sec:tdecomp}. Clearly these problems have deterministic
%polynomial time algorithms, the algorithms run in time exponential in
%$k$. As a result, when $k$ is part of the input, the \dfn{restricted
%OMD problem} has the potential to be difficult. For example, when the
%isostatic completion $H$ is required to be a 2-tree the restricted OMD
%problem is reducible to the maximum spanning series-parallel subgraph
%problem shown by \cite{cai1993spanning} to be NP-complete even if the input
%graph is planar of maximum degree at most 6. However, since the OMD
%problem has other input restrictions such as not having any proper
%isostatic subgraphs, it is not clear if the reverse reduction exists
%and hence it is unclear whether the OMD problem is NP-complete. The
%same holds for the restricted OMD problem where the isostatic
%completion $H$ is required to be a tree-decomposable graph of low
%Cayley complexity (i.e, have special, small DR-plans). One potential
%obstacle to an indecomposable graph $G$'s membership in the restricted
%OMD$_k$ for small $k$ is if $G$ is tri-connected and has large girth.
%In fact, 6-connected (hence rigid) graphs with arbitrarily large girth
%have been constructed in \cite{servatius2000rigidity}.
%
\subsection{Optimal Modification, Completion and Recombination: formal
connections}
%
The OMD problem is closely related to a well-studied problem of
completion of an under-constrained system to an isostatic one with a
small DR-plan.
\begin{observation}\label{obs:OC_to_OMD}
    The (decision version of) the \textbf{optimal completion problem
    (OC)} from \cite{sitharam2005combinatorial,joan-arinyo2003transforming,zhang-gao2006well} is OMD$_0$.
\end{observation}
In fact, a \dfn{restricted OC} problem was studied by \cite{joan-arinyo2003transforming}
requiring the completion to be tree-decomposable.
%It is not clear if
%the reverse reduction holds, i.e, is OMD reducible to OC?

@@

In order to connect the OR problem to OMD, when the input graph is
the isostatic graph at the DR-plan root, we do not consider the case
where the two child \dfn{solved subgraphs} (corresponding to already
solved subsystems) have a nontrivial intersection (in this case the
recombination is trivial). We only consider the case where no two
child solved subgraphs (resp. two root subgraphs when the input graph
is under-constrained) share more than 1 vertex. We replace such solved
subgraphs  by isostatic graphs as follows. If a solved subgraph shares
at most one vertex with the remainder of the graph, simply replace it
by an edge one of whose endpoints  is the shared vertex. Otherwise,
replace it by  a 2-tree graph of the shared vertices. Finally, we add
the additional restriction to the OM Problem that when any edge in a
solved subgraph is chosen among the $k$ edges to be removed, in fact
the entire solved subgraph must be removed  and all of its edges must
be counted in $k$.

>>>>

%In the recombination setting, the corresponding \dfn{restricted
%OMD$_k$  problem} requires the reduced graph $G'$ and its isostatic
%completion $H$ to be 2-trees as in Section \ref{sec:2-tree-reduction}
%or to be a low Cayley complexity tree-decomposable graph as in Section
%\ref{sec:tdecomp}. Clearly these problems have deterministic
%polynomial time algorithms, the algorithms run in time exponential in
%$k$. As a result, when $k$ is part of the input, the \dfn{restricted
%OMD problem} has the potential to be difficult. For example, when the
%isostatic completion $H$ is required to be a 2-tree the restricted OMD
%problem is reducible to the maximum spanning series-parallel subgraph
%problem shown by \cite{cai1993spanning} to be NP-complete even if the input
%graph is planar of maximum degree at most 6. However, since the OMD
%problem has other input restrictions such as not having any proper
%isostatic subgraphs, it is not clear if the reverse reduction exists
%and hence it is unclear whether the OMD problem is NP-complete. The
%same holds for the restricted OMD problem where the isostatic
%completion $H$ is required to be a tree-decomposable graph of low
%Cayley complexity (i.e, have special, small DR-plans). One potential
%obstacle to an indecomposable graph $G$'s membership in the restricted
%OMD$_k$ for small $k$ is if $G$ is tri-connected and has large girth.
%In fact, 6-connected (hence rigid) graphs with arbitrarily large girth
%have been constructed in \cite{servatius2000rigidity}.
%
\subsection{Optimal Modification, Completion and Recombination: formal
connections}
%
The OMD problem is closely related to a well-studied problem of
completion of an underconstrained system to an isostatic one with a
small DR-plan.
\begin{observation}\label{obs:OC_to_OMD}
    The (decision version of) the \textbf{optimal completion problem
    (OC)} from \cite{sitharam2005combinatorial,joan-arinyo2003transforming,zhang-gao2006well} is OMD$_0$.
\end{observation}
In fact, a \dfn{restricted OC} problem was studied by \cite{joan-arinyo2003transforming}
requiring the completion to be tree-decomposable.
%It is not clear if
%the reverse reduction holds, i.e, is OMD reducible to OC?

@@

In order to connect the OR problem to OMD, when the input graph is
the isostatic graph at the DR-plan root, we do not consider the case
where the two child \dfn{solved subgraphs} (corresponding to already
solved subsystems) have a nontrivial intersection (in this case the
recombination is trivial). We only consider the case where no two
child solved subgraphs (resp. two root subgraphs when the input graph
is underconstrained) share more than 1 vertex. We replace such solved
subgraphs  by isostatic graphs as follows. If a solved subgraph shares
at most one vertex with the remainder of the graph, simply replace it
by an edge one of whose endpoints  is the shared vertex. Otherwise,
replace it by  a 2-tree graph of the shared vertices. Finally, we add
the additional restriction to the OM Problem that when any edge in a
solved subgraph is chosen among the $k$ edges to be removed, in fact
the entire solved subgraph must be removed  and all of its edges must
be counted in $k$.

### 2015-02-15 doc/GMP2015/original_submission/s07_problempinning.tex
Made dir for original submission. Made dir for revision one and got it to compile with the new class file.

\section{Application: Finding completions of under-constrained glassy structures to isostatic}
\label{sec:bodypin}
% \bibliography{paper}

@@

We can use qusecs DR-plans to design materials such as disordered
graphene and silica bi-layers \cite{silica_bilayers}
\cite{sructure_of_2d_glass}. We will investigate a more specific problem in
a somewhat more general setting:
the problem of finding boundary conditions (additional constraints) to
add to an underconstrained monolayer to make it
isostatic.
This can be done in a number of ways:
(1) pin together 2 under-constrained monolayers in such a way that the resulting bi-layer becomes isostatic (see Figure \ref{fig:silica_glass});
(2) pin the boundary of (or in general, add constraints to) a layer (possibly a genus 0 monolayer) so that it becomes isostatic; or
(3) design a broader class of structures to ensure they are isostatic, self-similar (via some subdivision rule) and in addition isostatic at each level of the subdivision (see Figure \ref{fig:subdivision}).

>>>>

\section{Application: Finding completions of underconstrained glassy structures to isostatic}
\label{sec:bodypin}
% \bibliography{paper}

@@

We can use qusecs DR-plans to design materials such as disordered
graphene and silica bi-layers \cite{silica_bilayers}
\cite{sructure_of_2d_glass}. We will investigate a more specific problem in
a somewhat more general setting:
the problem of finding boundary conditions (additional constraints) to
add to an underconstrained monolayer to make it
isostatic.
This can be done in a number of ways:
(1) pin together 2 underconstrained monolayers in such a way that the resulting bi-layer becomes isostatic (see Figure \ref{fig:silica_glass});
(2) pin the boundary of (or in general, add constraints to) a layer (possibly a genus 0 monolayer) so that it becomes isostatic; or
(3) design a broader class of structures to ensure they are isostatic, self-similar (via some subdivision rule) and in addition isostatic at each level of the subdivision (see Figure \ref{fig:subdivision}).

### 2015-02-15 doc/GMP2015/revision_1/s00_abstract.tex
Made dir for original submission. Made dir for revision one and got it to compile with the new class file.

Crucial for the design and analysis of the abovementioned properties
is the recursive decomposition of diverse types of underlying 2D
geometric constraint systems that are \vemph{isostatic or
underconstrained (which we call collectively as \dfn{qusecs})}. While
the optimal recursive decomposition (\dfn{DR-planning}) problem is NP-
hard even for (possibly overconstrained) 2D bar-joint constraint
systems we describe an \candrpcomplexity algorithm  for qusecs. Besides
elucidating NP-hardness, the algorithm outputs \dfn{canonical} DR-
plans that meet various desirable, previously studied criteria. We
leverage recent results on Cayley configuration spaces to show that
the indecomposable systems -  that are solved at node of the optimal
DR-plan by recombining solutions to child systems - can be minimally
modified to become decomposable and have a small DR-plan, leading to
efficient realization algorithms. We show formal connections to well-
known problems such as completion of underconstrained systems. We
briefly discuss the modeling and analysis of two specific 2D layered
materials as applications of the above theory and algorithms. We
intend to make a software implementation and videos available upon
request and publicly available for the final version.
\end{abstract}

>>>>

Crucial for the design and analysis of the abovementioned properties
is the recursive decomposition of diverse types of underlying 2D
geometric constraint systems that are \vemph{isostatic or
underconstrained (which we call collectively as \dfn{qusecs})}. While
the optimal recursive decomposition (\dfn{DR-planning}) problem is NP-
hard even for (possibly overconstrained) 2D bar-joint constraint
systems we describe an \candrpcomplexity algorithm  for qusecs. Besides
elucidating NP-hardness, the algorithm outputs \dfn{canonical} DR-
plans that meet various desirable, previously studied criteria. We
leverage recent results on Cayley configuration spaces to show that
the indecomposable systems ---  that are solved at node of the optimal
DR-plan by recombining solutions to child systems --- can be minimally
modified to become decomposable and have a small DR-plan, leading to
efficient realization algorithms. We show formal connections to well-
known problems such as completion of underconstrained systems. We
briefly discuss the modeling and analysis of two specific 2D layered
materials as applications of the above theory and algorithms. We
intend to make a software implementation and videos available upon
request and publicly available for the final version.
\end{abstract}
